(Re)building cooperation: Effects of a cognitive intervention on cooperative behavior in games

### 2024-01-26 article.Rmd
statement anonymisation

Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
Funding: Author 1 was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1. Author 3 acknowledges support by the UCLH NIHR BRC. He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
Ethics: This research received approval from a local ethics board (ID:21029/001).
Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available. The design and analysis plans were not preregistered.

@@

prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))

cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
```

@@

@@

@@

\newpage
```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels. The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social. B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection. The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states. As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
library(magick)

# Display the combined image
plot(final_image)
```
\newpage

>>>>

Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
Funding: Author 1 was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1. Author 3 acknowledges support by the UCLH NIHR BRC. He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
Ethics: This research received approval from a local ethics board (ID:21029/001).
Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available on: https://github.com/ismailg/coax_psych_science. The design and analysis plans were not preregistered.

@@

#prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
#cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
```

@@

# Subset the data for pre and post measurements
pre_data <- avg_ret_df$ret_pct[avg_ret_df$gameNum.f == 'pre']
post_data <- avg_ret_df$ret_pct[avg_ret_df$gameNum.f == 'post']

# Calculate the correlation
correlation <- cor(pre_data, post_data, use = "complete.obs")

# Print the result
print(correlation)

@@

```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels. The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social. B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection. The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states. As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
library(magick)

# Display the combined image
plot(final_image)
```

@@
